\documentclass[12pt,paper=a4,oneside,cleardoubleage=plain,final]{report}

\usepackage[utf8]{inputenc}

% Hyperreferencing and citations
\usepackage{hyperref}
\usepackage[all]{hypcap}    %for going to the top of an image when a figure reference is clicked
\hypersetup{
	colorlinks,
	citecolor=black,
	filecolor=blue,
	linkcolor=black,
	urlcolor=blue
}

\usepackage{graphicx}
\graphicspath{{images/}}

\usepackage{natbib} %for references

\usepackage{xcolor}
\usepackage{listings}
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
	backgroundcolor=\color{backcolour},   
	commentstyle=\color{codegreen},
	keywordstyle=\color{magenta},
	numberstyle=\tiny\color{codegray},
	stringstyle=\color{codepurple},
	basicstyle=\ttfamily\footnotesize,
	breakatwhitespace=false,         
	breaklines=true,                 
	captionpos=b,                    
	keepspaces=true,                 
	numbers=left,                    
	numbersep=5pt,                  
	showspaces=false,                
	showstringspaces=false,
	showtabs=false,                  
	tabsize=2
}

\lstset{style=mystyle}
%for code highlighting


% TABLE OF CONTENTS
\usepackage{titletoc}%
\titlecontents{chapter}% <section-type>
[0pt]% <left>
{\bfseries}% <above-code>
{\chaptername\ \thecontentslabel:\quad}% <numbered-entry-format>
{}% <numberless-entry-format>
{\hfill\contentspage}% <filler-page-format>



\usepackage{enumitem} %% for enumerate a b c]
\usepackage{setspace}
% single spacing for table of contents

\setlength{\parindent}{3em}

\usepackage{blindtext}
\usepackage[left=1in, right=1in, top=1in, bottom=1in, includefoot, headheight=13.6pt]{geometry}
\usepackage{soul}
% set times new roman
\usepackage{newtxtext, newtxmath}
\usepackage{floatrow} % 2 images on one row

\usepackage[explicit, pagestyles]{titlesec}

\newcommand{\comment}[1]{}


\setcounter{tocdepth}{4}
\setcounter{secnumdepth}{4}


\newpagestyle{mine}{%
	
	\setfoot{}{}{\thepage}}%

\renewpagestyle{plain}{%
	\setfoot{}{}{\thepage}}%


% Update chapter title format
\titleformat{\chapter}[display]
{\normalfont\fontsize{12pt}{14pt}\selectfont\bfseries\centering} % 12pt chapter title
{\normalfont Chapter \thechapter} % Chapter label
{1em} % Space between the number and the title
{#1} % Title text

\titlespacing{\chapter}{0pt}{-32pt}{1cm} % Adjust spacing for chapters

% Update section title format
\titleformat{\section}
{\normalfont\fontsize{12pt}{14pt}\selectfont\bfseries} % 12pt section title
{\thesection} % Section number
{1em} % Space between number and title
{#1} % Title text

\titlespacing{\section}{0pt}{1.5ex plus .1ex}{1.5ex plus .1ex} % Adjust spacing for sections

% Update subsection title format
\titleformat{\subsection}
{\normalfont\fontsize{12pt}{14pt}\selectfont\bfseries} % 12pt subsection title
{\thesubsection} % Subsection number
{1em} % Space between number and title
{#1} % Title text

\titlespacing{\subsection}{0pt}{1.25ex plus .1ex}{1.25ex plus .1ex} % Adjust spacing for subsections
\pagestyle{mine}

\begin{document}
\input{chapters/title}
\doublespacing

\pagenumbering{roman}
\clearpage
\setcounter{page}{2}

\chapter*{DECLARATION}
\noindent
I, TEKENA SOLOMON admit that I did all the work on this project by myself and that it has never been turned in for credit toward a degree. The report is also all written in my own words, except for a few quotes that were properly credited and acknowledged. Ms. A. E. Babalola was my supervisor in charge of supervising both the project work and the report.

\vspace{10mm}
\begin{tabular}{@{}p{.5in}p{2in}@{}}
	Signature: & \hrulefill \\
	& Tekena Solomon \\
\end{tabular}
\addcontentsline{toc}{chapter}{DECLARATION}

\chapter*{CERTIFICATION}
\noindent
\normalsize This is to certify that \textbf{TEKENA SOLOMON} with matriculation number AUL/SCI/18/00256 carried out this project work titled 'HEART DISEASE PREDICTION USING MACHINE LEARNING TECHNIQUES' under supervision and that this project work has not been submitted before. \\[1.0cm]

\vspace{0.8cm}

%\centering

\noindent
\begin{tabular}{@{}p{0.5\textwidth}p{0.5\textwidth}@{}}
	Supervisors' Name & \\[0.2cm]
	Ms. A. E. Babalola & Signature \& Date\dotfill \\[1cm]
	Head Of Department & \\[0.2cm]
	Dr.  J. B. Odili & Signature \& Date\dotfill \\[1cm]
	Prof. A. P Adewole & \\[0.2cm]
	(External Supervisor) & Signature \& Date\dotfill \\
\end{tabular}

\vfill


\addcontentsline{toc}{chapter}{CERTIFICATION}

\chapter*{ACKNOWLEDGEMENTS}
\noindent
I want to thank God, for giving me the strength and wisdom to complete this project, my parents,for their constant support and to my supervisor Miss Asegunloluwa Babalola for her constant support.
\addcontentsline{toc}{chapter}{ACKNOWLEDGEMENTS}

\chapter*{DEDICATION}
\noindent
This project is dedicated to my mum and dad, who has always been there for me and encouraged me to keep going, even when times were tough; to my friends Allwell and Sahil, who have been there for me through thick and thin.
\addcontentsline{toc}{chapter}{DEDICATION}


\chapter*{ABSTRACT}
\noindent
Heart disease, a leading global health concern, necessitates accurate and timely diagnosis. This research presents a machine learning-based system for predicting cardiovascular disease, utilizing a comprehensive dataset derived from multiple sources. The system employs supervised learning algorithms, including Naive Bayes, Decision Tree, Logistic Regression, and K-Nearest Neighbors. To evaluate the system's performance, we employed Stratified K-Fold cross-validation and assessed accuracy using the Area Under the ROC Curve (AUC). The K-Nearest Neighbors algorithm demonstrated the highest performance, achieving a peak accuracy of 91.6\%. This system offers a valuable tool for early detection and risk assessment of heart disease, empowering individuals and healthcare professionals to make informed decisions regarding prevention and treatment. By providing timely insights, this system can contribute to improving cardiovascular health outcomes and reducing the burden of heart disease.
\addcontentsline{toc}{chapter}{ABSTRACT}


{
	\onehalfspacing
	\renewcommand{\contentsname}{Table of Contents}
	\tableofcontents
	%\listoftables
	\listoffigures
	%\lstlistoflistings
}



%\chapter*{Keywords}
%keywords here?


\chapter{Introduction}
\pagenumbering{arabic}
\setcounter{page}{1}
\input{chapters/introduction}

\chapter{Literature Review}
\input{chapters/chapter02}

\chapter{Research Methodology}
\label{chap:3}
\input{chapters/chapter03}

\chapter{Implementation and Results}
\label{chap:4}
\input{chapters/chapter04}

\comment{summary, conclusion and recommendation}
\chapter{Conclusion}
\input{chapters/conclusion}


\comment {
Definition. An appendix contains supplementary material that is not an essential part of the text itself but which may be helpful in providing a more comprehensive understanding of the research problem or it is information that is too cumbersome to be included in the body of the paper.
}

\renewcommand{\bibname}{References}
\bibliographystyle{apalike}
\bibliography{chapters/references}

\appendix
\input{chapters/appendix}

\end{document}